---
title: "Code"
author: "BHMQ3"
date: "2023-01-03"
output: html_document
---

Libraries

```{r}
library(tidyverse)
library(sf)
library(tmap)
library(nngeo)
library(spdep)
library(sp)
library(data.table)
library(janitor)
library(spatstat)
library(gstat)
library(devtools)
install_github('mcooper/moranfast')
library(moranfast)
library(broom)
library(rgeos)
library(maptools)
library(tmaptools)
library(geoR)
```

Loading CSV Data

```{r}
metro <- read_csv("DELHI_METRO_DATA.csv",  show_col_types = FALSE)
metro <- metro %>% drop_na()
metro <-metro%>%
  
  st_as_sf(., coords = c("Longitude", "Latitude"), 
           crs = 7760)

rent <- read_csv("June_8_data_metro_closest_stations.csv",  show_col_types = FALSE)
rent <- rent %>% drop_na()
rent <- rent%>%
  
  st_as_sf(., coords = c("longitude", "latitude"), 
           crs = 7760)
```

Loading Shapefiles

```{r}
wards <- st_read("Delhi_Wards-SHP/Delhi_Wards.shp", crs=7760)
highway <- st_read("delhi_highway/delhi_highway.shp", crs=7760)
```

Maps prior to overlaying data

```{r}
tm_shape(wards) +
  tm_polygons(col = NA, alpha = 0.5)

tm_shape(highway) +
  tm_lines(col = NA, alpha = 0.5)
 
tm_shape(highway) +
  tm_lines(col = NA, alpha = 0.5) +
  tm_shape(wards) +
  tm_polygons(col = NA, alpha = 0.5)
```


Mapping Metro locations on 3 levels

```{r}
tm_shape(wards) +
  tm_polygons(col = NA, alpha = 0.5) +
  tm_shape(metro) +
  tm_dots(col = "red")

tm_shape(highway) +
  tm_lines(col = NA, alpha = 0.5) +
  tm_shape(metro) +
  tm_dots(col = "red")

tm_shape(highway) +
  tm_lines(col = NA, alpha = 0.5) +
  tm_shape(wards) +
  tm_polygons(col = NA, alpha = 0.5) +
  tm_shape(metro) +
  tm_dots(col = "red")
```

Mapping Rent locations on 3 levels

```{r}
tm_shape(wards) +
  tm_polygons(col = NA, alpha = 0.5) +
  tm_shape(rent) +
  tm_dots(col = "gold")

tm_shape(highway) +
  tm_lines(col = NA, alpha = 0.5) +
  tm_shape(rent) +
  tm_dots(col = "gold")

tm_shape(highway) +
  tm_lines(col = NA, alpha = 0.5) +
  tm_shape(wards) +
  tm_polygons(col = NA, alpha = 0.5) +
  tm_shape(rent) +
  tm_dots(col = "gold")
```

Combined map prior to subsetting

```{r}
tm_shape(highway) +
  tm_lines(col = NA, alpha = 0.5) +
  tm_shape(wards) +
  tm_polygons(col = NA, alpha = 0.5) +
  tm_shape(rent) +
  tm_dots(col = "gold") +
  tm_shape(metro) +
  tm_dots(col = "red")
```

Subsetting and new map

```{r}
metro_fil <- metro[wards,]
rent_fil <- rent[wards,]
```


```{r}
tm_shape(highway) +
  tm_lines(col = NA, alpha = 0.5) +
  tm_shape(wards) +
  tm_polygons(col = NA, alpha = 0.5) +
  tm_shape(rent_fil) +
  tm_dots(col = "gold") +
  tm_shape(metro_fil) +
  tm_dots(col = "red")
```
 Rent cost according to cost of living
 
```{r}
 in_bhk3<-rent_fil%>%
  filter((price >  48000))

out_bhk3<-rent_fil%>%
  filter((price < 27000))

in_bhk1<-rent_fil%>%
  filter((price >  19000))

out_bhk1<-rent_fil%>%
  filter((price < 11000))
```
  
```{r}
tm_shape(wards) +
  tm_polygons(col = NA, alpha = 0.5) +
  tm_shape(metro_fil) +
  tm_dots(col = "red") +
  tm_shape(in_bhk3) +
  tm_dots(col = "green")

tm_shape(wards) +
  tm_polygons(col = NA, alpha = 0.5) +
  tm_shape(metro_fil) +
  tm_dots(col = "red") +
  tm_shape(in_bhk1) +
  tm_dots(col = "pink")

tm_shape(wards) +
  tm_polygons(col = NA, alpha = 0.5) +
  tm_shape(metro_fil) +
  tm_dots(col = "red") +
  tm_shape(out_bhk3) +
  tm_dots(col = "cyan")

tm_shape(wards) +
  tm_polygons(col = NA, alpha = 0.5) +
  tm_shape(metro_fil) +
  tm_dots(col = "red") +
  tm_shape(out_bhk1) +
  tm_dots(col = "yellow")
```
```{r}
metro_dist <- rent_fil[c("closest_mtero_station_km")]

price <- rent_fil[c("price")]

price_comp <- rent_fil[c("closest_mtero_station_km", 'price' )]

```

Plotting centroids from the wards file

```{r}
coordsW <- wards%>%
  st_centroid()%>%
  st_geometry()
  
plot(coordsW,axes=TRUE)

LWard_nb <- wards %>%
  poly2nb(., queen=T)

plot(LWard_nb, st_geometry(coordsW), col="red")

plot(wards$geometry, add=T)

Lward.lw <- LWard_nb %>%
  nb2mat(., style="B")

sum(Lward.lw)
```
Plotting centroids using KNN

```{r}
knn_wards <-coordsW %>%
  knearneigh(., k=4)

LWard_knn <- knn_wards %>%
  knn2nb()

plot(LWard_knn, st_geometry(coordsW), col="blue")

Lward.knn_4_weight <- LWard_knn %>%
  nb2listw(., style="W")
```

Running a Moran's I test using a custom program

```{r}
dfrent <- read_csv("June_8_data_metro_closest_stations.csv", show_col_types = FALSE)
moranfast(dfrent$closest_mtero_station_km, dfrent$longitude, dfrent$latitude, )
```
simple linear regression - p-value shows 10% chance of rejecting null hypothesis

```{r}
summary(linearreg <- lm(price ~ closest_mtero_station_km, data = price_comp))
```
poission regression

```{r}
summary(poissonreg <- glm(price ~ closest_mtero_station_km, family="poisson", data=price_comp))
```
